Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs

### 2015-04-13 slides/esop-termination.tex
Experiments

\begin{frame}{Experiments}

>>>>

\begin{frame}{Experiments}
We implemented the {\sc Juggernaut} tool, which is slow but unstoppable.

We compared to {\sc ARMC} on a set of 47 benchmarks taken from SVCOMP and our own
regression tests.

\begin{center}
 \begin{tabular}{|l||l|l|}
  \hline
  & {\sc ARMC} & {\sc Juggernaut} \\
  \hline
  \hline
  Correct & 28 & 35 \\
  Incorrect for bitvectors & 3 & 0 \\
  Unknown & 13 & 0 \\
  Timeout & 3 & 12 \\
  \hline
  Median time (s) & 0.09 & 2.2 \\
  \hline
 \end{tabular}
\end{center}
